Visual narratives of the Covid-19 pandemic

### 2022-09-02 Review/Edits/JDSSV_manuscript_submitted.tex
Edits and original submission

\documentclass[article]{jdssv}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
}

\begin{document}
% \SweaveOpts{concordance=TRUE}
<<include=FALSE, cache=FALSE, echo=FALSE, purl=FALSE>>=
library(knitr)
opts_chunk$set(comment = NA, size = 'footnotesize', prompt = TRUE, highlight = FALSE, 
               cache = TRUE, crop = TRUE, concordance = FALSE, fig.align='center',
               fig.path='Figures_R/fig-',out.width="0.4\\textwidth", 
               message = F, error = F, warning = F, echo = F)
opts_knit$set(out.format = "latex")
knit_hooks$set(crop = hook_pdfcrop)
options(width = 80, prompt = "R> ", continue = "    ", digits = 3)
thm <- knit_theme$get('default')
Sys.setenv(TEXINPUTS=getwd(),
           BIBINPUTS=getwd(),
           BSTINPUTS=getwd())
knit_theme$set(thm)
@

<<get-nyt-data, include = F>>=

# Read in the data from NYT
library(tidyverse)
library(lubridate)
library(zoo)
library(ggrepel)
library(gridExtra)
cvstate <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")

if (!dir.exists("Data")) dir.create("Data")
write_csv(cvstate, file = "Data/covid-data-nyt.csv") # Save data just in case

cvstate <- cvstate %>%
  group_by(state, fips) %>%
  mutate(date_100th_case = min(date[cases >= 100]),
         days_100th_case = date - date_100th_case,
         daily_cases = cases - lag(cases, 1, default = 0),
         week_avg_cases = rollmean(cases, 7, align = "right", fill = c(0, NA, NA), na.pad = T, na.rm = T),
         daily_avg_cases = rollmean(daily_cases, 7, align = "right", fill = c(0, NA, NA), na.pad = T, na.rm = T),
         daily_deaths = deaths - lag(deaths, 1, default = 0),
         week_avg_deaths = rollmean(deaths, 7, align = "right", fill = c(0, NA, NA), na.pad = T, na.rm = T),
         daily_avg_deaths = rollmean(daily_deaths, 7, align = "right", fill = c(0, NA, NA), na.pad = T, na.rm = T)) %>%
  ungroup() %>%
  mutate(state = factor(state))

download.file("https://www2.census.gov/programs-surveys/popest/tables/2010-2019/state/totals/nst-est2019-01.xlsx", destfile = "Data/census_pop_state.xlsx", quiet = T, mode = "wb")
pop_data <- readxl::read_xlsx("Data/census_pop_state.xlsx", col_names = c("state", "pop2019"), col_types = c("text", rep("skip", 11), "numeric"), skip = 9) %>%
  mutate(state = str_remove(state, "[[:punct:]]"))

cvstate <- left_join(cvstate, pop_data, by = "state")

my_theme <- theme_bw() + 
  theme(plot.background = element_rect(fill = "transparent", colour = NA), 
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),
        axis.text.y = element_text(angle = 90, hjust = 0.5)) 
theme_set(my_theme)
@

<<colourpal, include = F>>=
# Including this for temporary compatibility - we may want to use *shudder* viridis?
main_colours <- c("#d00000", "#f5f1e7", "#c7c8ca")

# use as accents
secondary_colours <- c("#001226", "#249ab5")

# These are only to be used for infographics/charts
tertiary_colours <- c("#bccb2a", "#f58a1f", "#005d84", "#ffd74f", "#a5228d")

colour_palette <- c("#d00000", "#249ab5",  "#1B8500", "#f58a1f", "#a5228d", "#001226", "#B1EB66", "#005d84", "#c25700")

heat_colour_palette <- c("#ffd74f", "#f58a1f", "#c25700", "#d00000", "#9D0000", "#6A0000")

blueseqpal <- c("001226", "06293E", "0C3F56", "12566E", "186D85", "1E839D", 
                "249AB5", 
                "39ABC1", "4EBCCE", "64CDDA", "79DDE6", "8EEEF3", "A3FFFF") %>% 
  paste0("#", .) %>% rev()

blueseqpal_lt <- rev(c("#B2FFFF", "#C2FFFF", "#D1FFFF", "#E0FFFF", "#F0FFFF"))

darkblueseqpal <- colorspace::darken(blueseqpal, .2)
lightblueseqpal <- colorspace::lighten(blueseqpal, .2)
@
%% -- Introduction -------------------------------------------------------------

>>>>

\documentclass[article]{jdssv}\usepackage[]{graphicx}\usepackage[]{xcolor}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
% \SweaveOpts{concordance=TRUE}

%% -- Introduction -------------------------------------------------------------

### 2022-09-02 Review/Edits/initial-submission.tex
Edits and original submission

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
    email: \email{susan.vanderplas@unl.edu}
  Susan Vanderplas\\
  Department of Statistics\\
  University of Nebraska–Lincoln\\
  349A Hardin Hall \\
  Lincoln, NE 68583-0963, USA\\
  E-mail: \email{susan.vanderplas@unl.edu}\\
  URL: \url{https://statistics.unl.edu/susan-vanderplas}\\
\ \\
%}
%
%\Address{
  Adalbert F.X. Wilhelm\\
  Department of Psychology and Methods\\
  Jacobs University Bremen gGmbH\\
  Campus Ring 1\\
  28759 Bremen, Germany\\
  E-mail: \email{a.wilhelm@jacobs-university.de}\\
  URL: \url{http://www.jacobs-university.de/directory/wilhelm}
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
% \SweaveOpts{concordance=TRUE}

>>>>

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
% \SweaveOpts{concordance=TRUE}
